---
title: "Give a try at shiny application"
author: "Nadia S."
date: "6/23/2020"
output: ioslides_presentation
widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Guidelines and short introduction
In the present assignment, an application has to be build using the library shiny. 
The app should contain at least one of these parameters: radiobuttons, buttons, textboxes, etc.   

The application should have a documentation to guide the user through the application. 

The dataset is downloaded from Kaggle and here is the  [link](https://www.kaggle.com/ronitf/heart-disease-uci). Only a few parameters are used in the application. Most of the variables are factors which don't provide much information. 

In short, the application displays a graph of some parameters that can be selected by the user. A regression line is displayed to show the correlation between x and y. The correlation factor is also displayed along the plot.


## Codebook of the parameters used
- age: The person's age in years
- sex: The person's sex (1 = male, 0 = female)
- cp: The chest pain experienced (Value 1: typical angina, Value 2: atypical angina, Value 3: non-anginal pain, Value 4: asymptomatic)
- trestbps: The person's resting blood pressure (mm Hg on admission to the hospital)
- chol: The person's cholesterol measurement in mg/dl
- fbs: The person's fasting blood sugar (> 120 mg/dl, 1 = true; 0 = false)
- thalach: The person's maximum heart rate achieved
- target: Heart disease (0 = no, 1 = yes)


## Application
The application is very basic and show a plot of some features from the dataset. The user can select some features from the dataset using a drop-down list and a plot is instantly generated. The correlation factor is also calculated and displayed under the plot.

The dataset needs a bit of cleaning and this is done by the following code lines. 
```{r}
  data <- read.table("data_heart_disease_uci.txt", header = TRUE)
  data$sex <- ifelse(data$sex == 1, "Male", "Female")
  data$fbs <- ifelse(data$fbs == 1, "high", "Normal")
  data$target <- ifelse(data$target == 1, "Yes", "No")
```

## Application details
The input provided by the user for the x and y axis, as well as the variable are stored in a reactive function. A data frame is generated and pushed to create a plot. The plot is then drawn and showed to the user. The correlation factor is displayed as well.

The application can be implemented with a prediction model in order to determine people that are risk of developing a heart disease. 


